### 2022-07-09 supplemental/OJEMB Supplementary Material.tex
Add to supplementary info

@@

To determine a suitable stimulus generation method,
we performed a hyperparameter sweep over hyperparameters
of nine different stimulus generation methods.
We used an \textit{in-silico} model of the experiment,
matching against an American Tinnitus Association tinnitus example,
as in the human experiment.

@@

\begin{equation}
  y = \mathrm{sgn}(\Psi * \bar{x})
\end{equation}

@@

Reconstructions were computed using linear regression and compressed sensing
and reconstruction accuracy was measured using Pearson's $r^2$ vs. the target signal.

% n_bins: [10 30 100 200 300]
% bin_prob: [0.1000 0.3000 0.5000 0.8000]
% amplitude_mean: -35
% amplitude_var: [5 10 20]
% n_bins_filled_mean: [1 3 10 20 30]
% n_bins_filled_var: [0.0100 1 3 10]
% min_bins: [1 3 10 20 30]
% max_bins: [10 20 30 50]

>>>>

\usepackage{siunitx}
\sisetup{parse-numbers = false}

@@

To determine a suitable stimulus generation method,
we performed a hyperparameter sweep over
nine different stimulus generation methods.
We used an \textit{in-silico} model of the experiment,
with an artificial subject, but matched against American Tinnitus Association (ATA) tinnitus examples,
as in the human experiment.

@@

\begin{equation}
  y = \mathrm{sgn}(\Psi \bar{x})
\end{equation}

@@

Reconstructions were computed using linear regression and compressed sensing
(\cf the main paper)
and reconstruction accuracy was measured using Pearson's $r^2$ vs. the target signal.

Fine-tuning of parameters proceeded iteratively,
bearing in mind both the performance of the stimulus generation methods
in the \textit{in-silico} experiment as well as computational efficiency,
qualitative distinguishability of stimuli from each other by a human listener,
and viability of compressed sensing as an efficiency enhancement.
This process resulted in $n \_ bins$ being fixed to $100$ and
the number of trials in the \textit{in-silico} experiment being set to $1000$.

\begin{table}[ht]
	\begin{center}	
		\small
		\resizebox{1\columnwidth}{!}{
			\begin{tabular}{l S[table-format=12.2] S[table-format=12.2] S[table-format=12.2] S[table-format=6.2] S[table-format=6.2] S[table-format=6.2] S[table-format=6.2]}	
				\multicolumn{7}{c}{\textsc{Hyperparameter Sweep Results}} \\
				\hhline{=======}
				Stimulus Type & n \_ bins \_ filled \_ mean & n \_ bins \_ filled \_ var & min \_ bins & max \_ bins & CS \_ r^2 & LR \_ r^2 \\ 
				\hline
				Gaussian Prior    & 20 & 1 & & & 0.83 & 0.86 \\
        Uniform Prior     & & & 30 & 30 & 0.82 & 0.86 \\
        Uniform Prior     & & & 20 & 20 & 0.82 & 0.86 \\
        Gaussian Prior    & 20 & 1 & & & 0.82 & 0.86 \\
        Gaussian Prior    & 12 & 0.01 & & & 0.81 & 0.83 \\
				\hhline{=======}
			\end{tabular}
		}
	\end{center}
%\normalsize
	\caption{Top-5 stimulus generation methods by $r^2$ score averaged over
  buzzing, electric, roaring, screeching, and static tinnitus examples,
  with $n \_ bins = 100$ and $n \_ trials = 1000$.
  }
	\label{tbl:hparam_results}
\end{table}

%       stimuli_type       n_bins_filled_mean    n_bins_filled_var    min_bins    max_bins    mean_r2_cs    mean_r2_linear
%     _________________    __________________    _________________    ________    ________    __________    ______________

%     {'GaussianPrior'}            20                  0.01             NaN         NaN          0.83            0.86     
%     {'UniformPrior' }           NaN                   NaN              30          30          0.82            0.86     
%     {'UniformPrior' }           NaN                   NaN              20          20          0.82            0.86     
%     {'GaussianPrior'}            20                     1             NaN         NaN          0.81            0.86     
%     {'GaussianPrior'}            10                  0.01             NaN         NaN          0.81            0.83     
%     {'GaussianPrior'}            30                     1             NaN         NaN           0.8            0.84     
%     {'UniformPrior' }           NaN                   NaN              10          10           0.8            0.83     
%     {'GaussianPrior'}            10                     1             NaN         NaN          0.79            0.83     
%     {'UniformPrior' }           NaN                   NaN              20          30          0.79            0.79     
%     {'GaussianPrior'}            30                  0.01             NaN         NaN          0.79            0.86

Table \ref{tbl:hparam_results} shows the top 5 best-performing methods
in the \textit{in-silico} experiment.
Gaussian Prior and Uniform Prior outperform all other methods,
with 10-30\% of bins being filled.
The variance of the number of filled bins for top-performing methods
is extremely low.
Due to rounding to the nearest integer, a Gaussian Prior method with very low variance
converges to a Uniform Prior method with equal min and max bin parameters.
In the main paper, we used the Uniform Prior method with 30 filled bins ($min \_ bins = max \_ bins = 30$).

\section{Sparsity of ATA Tinnitus Examples}

A necessary condition for compressed sensing to produce reconstructions results
beyond the Shannon-Nyquist limit is that the signal to be reconstructed is sparse in some basis
\cite{taghoutiCompressedSensing2020}.
A signal is considered to be at least $k$ sparse when it has at most $k$ nonzero elements.
A signal is considered $k$-sparse under some basis, when a basis-transformed version
of that signal is $k$-sparse.
Here we show that the 8,193-dimensional ATA example tinnitus spectra are sparse under
the discrete cosine basis.
The signal representation in the basis is produced by computing its discrete cosine transform (DCT).
We computed the DCT of each ATA example spectrum
and set all but the top 32 DCT-frequencies to zero
before taking the inverse transform back to the Fourier domain.
Figure \ref{fig:target_signal_sparsity_1}
shows that while some high-frequency information was lost,
that the 32-sparse signal preserves the salient information of the signal.
The tonotopic bin representation is also sparse under the discrete cosine basis
(Fig. \ref{fig:target_signal_sparsity_2}).
The sparsity value $k=32$ was chosen by examining the decay of the sorted power spectrum
of the tinnitus Fourier spectra in the discrete cosine basis (Fig. \ref{fig:target_signal_sparsity_3}).
We see that the power of the signal rapidly decays after only a few DCT-frequencies.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/target_signal_sparsity_1.eps}
	\caption{Tinnitus signals are approximately sparse.
    Each subfigure plots the true spectrum of an ATA tinnitus example
    in blue (8,193 nonzero dimensions) and a 32-sparse (32 non-zero dimensions)
    approximation in green.
    The sparse signal is a low-pass filtered version of the original signal
    that retains the salient dynamics.
    \textbf{(a)} through \textbf{(f)} correspond to
    buzzing, electric, roaring, static, tea kettle, and screeching ATA examples
    respectively.}
	\label{fig:target_signal_sparsity_1}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/target_signal_sparsity_2.eps}
	\caption{Tonotopic bin representations of tinnitus signals are approximately sparse
    in the DCT basis.
    Each subfigure plots the tonotopic bin representation of an ATA tinnitus spectrum
    in blue (100 nonzero dimensions) and the bin representation of a 10-sparse
    approximation in red (10 nonzero dimensions).
    The sparse signal is a low-pass filtered version of the original signal
    that retains the salient dynamics.
    \textbf{(a)} through \textbf{(f)} correspond to
    buzzing, electric, roaring, static, tea kettle, and screeching ATA examples
    respectively.}
	\label{fig:target_signal_sparsity_2}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/target_signal_sparsity_3.eps}
	\caption{DCT-transformed tinnitus spectra have high power in a few frequencies
  and low power elsewhere. \textbf{a} shows the power spectrum of DCT-transformed
  ATA tinnitus example Fourier spectra. \textbf{b} shows the highest 40 DCT frequencies
  in ranked order, illustrating a sharp decay to zero, indicating sparsity
  of tinnitus spectra in the DCT basis.}
	\label{fig:target_signal_sparsity_3}
\end{figure}
